Maps and spatial stats demo

### 2024-10-10 recaptureanalysis/Mapdemo.qmd
Edited plots for 2019 synthesis and did a bit with biofouling bugs

The output is a matrix with distance between each of the points in meters.

```{r}
print(fishdistances)
```

>>>>

The output is a matrix with distance between each of the points in meters. To calculate the average distance between each pair of fish, take the mean of the lower triangle of the matrix.

```{r}
print(fishdistances)

```

Now let's reorganize it so we can take the mean

```{r}
#take out the lower triangle so we just have the upper triangle
 fishdistances[lower.tri(fishdistances, diag = T)] = NA

  fishd = as.data.frame(fishdistances) %>%
    mutate(Fish1 = row.names(fishdistances)) %>%
    pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance))

  print(fishd)
```

THat was the distance between fish. The distance from a particular point is a bit easier. If the coordinates of Rio Vista are 38.1247 and -121.6995, we can do this -

```{r}
RV = data.frame(Latitude = 38.1247, Longitude = -121.6995)

DistRV = GGdist(Water_map = spacetools::Delta, Points = testdata, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = RV)

DistRV
```
